Ceph Parallel File System Evaluation Report

### 2013-11-06 report.tex
Add sponsorship info

@@

@@

%\maketitle
%\authorrunning{}
%\titlerunning{}

>>>>

\usepackage{tikz}

@@

\title{Ceph Parallel File System Evaluation Report}
\date{}
\newcommand\sponsortext{%
This research was supported by, and used the
resources of, the Oak Ridge Leadership Computing Facility, located in the
National Center for Computational Sciences at ORNL, which is managed by UT
Battelle, LLC for the U.S. DOE (under the contract No. DE-AC05-00OR22725).}

\newcommand\sponsornotice{%
\begin{tikzpicture}[remember picture,overlay]
\node[anchor=south,yshift=30pt] at (current page.south)
{\fbox{\parbox{\dimexpr\textwidth-\fboxsep-\fboxrule\relax}{\sponsortext}}};
\end{tikzpicture}%
}

@@

% \maketitle
%\authorrunning{}
%\titlerunning{}

\sponsornotice
